MSDS6372Project1

### 2021-01-25 MSDS6372Project1.Rmd
fixing train/validate/test set split: line 231 to line 253

#Without transformation, split dataset
set.seed(111)
train.test.index<-sample(1:dim(CarData)[1],10723,replace=F)
train.test = CarData[train.test.index,]
validate = CarData[-train.test.index,]
set.seed(112)
train.index = sample(1:dim(train.test)[1],9531,replace=F)
train = train.test[train.index,]
test = train.test[-train.index,]

str(train)

# Use Forward variable selection method to select possible variables as predictors
library(leaps)
reg.fwd=regsubsets(MSRP~.,data=train,method="forward",nvmax=955)
par(mfrow=c(1,3))
bics<-summary(reg.fwd)$bic
plot(1:956,bics,type="l",ylab="BIC",xlab="# of predictors")
index<-which(bics==min(bics))
points(index,bics[index],col="red",pch=10)

>>>>

######### Try Something else to split data ############
# First 842 are Models that only have 5 observations or less
ModelList = CarData%>% group_by(Model) %>% mutate(ModelCount = n()) %>% arrange(ModelCount)
#arrange(ModelList,desc(count))%>%print(n = Inf)
# Can only split train/test/validate set on Models that has 6 observations or more
ModelList = ModelList[,-27]
Not.Able.To.Split = ModelList[(1:842),]
Able.To.Split = ModelList[-(1:842),]

# Split Train, test, validate based on able to Train Data...
set.seed(111)
validate.set.index<-sample(1:dim(Able.To.Split)[1],1191,replace=F)
validate = Able.To.Split[validate.set.index,]
remains1 = Able.To.Split[-validate.set.index,]
set.seed(112)
test.index = sample(1:dim(remains1)[1],1191,replace=F)
test = remains1[test.index,]
train = remains1[-test.index,]

# Joining train set with dataset that been left out
train = bind_rows(train,Not.Able.To.Split)
dim(train)

str(train)
str(CarData)
# Use Forward variable selection method to select possible variables as predictors
library(leaps)
reg.fwd=regsubsets(MSRP~.,data=train,method="forward",nvmax=955)
par(mfrow=c(1,3))
bics<-summary(reg.fwd)$bic
plot(1:956,bics,type="l",ylab="BIC",xlab="# of predictors")
index<-which(bics==min(bics))
points(index,bics[index],col="red",pch=10)
